---
title: "Massachusetts Honey Harvest 2015-2017"
author: "Stephanie M. Davis. s.davis@bestbees.com"
date: "June 27, 2018"
output:
  pdf_document:
    keep_tex: yes
  html_notebook: default
  html_document:
    df_print: paged
---
# Import the requisite packages
```{r}
library(readxl)
#library(plyr)
library(tidyverse)
```

# Read the excel data file into a tibble
```{r}
noah_bar <- read_xlsx("USEthis_honey_june27.xlsx")
dput(noah_bar)
```

# Chart Weight by Year using geom_col
```{r message=TRUE, warning=TRUE}
ggplot(data = noah_bar,mapping = aes(x = Year, y = Weight, fill = Location)) + geom_col(position = "dodge")
```
# How do I plot each year's weight total by the top 5 locations? 
# i.e. The locations comprising the 5 highest weight totals for each year. For example, in 2015: Massachuetts aggregate honey harvest was 4014 lbs and Boston - 944 lbs., Cape Cod - 472 lbs., Duxbury - 328 lbs.,Medfield - 253 lbs., Cambridge - 204 lbs. were the top 5 2015 local producers

# SERENDIPITY - added the color aes and mapped Location variable to it.
# Not what I want but it's a start

```{r}
#ggplot(data = noah_bar,mapping = aes(x = Year, y = Weight )) + #geom_col(mapping = aes(color = Location))
```

